\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Update on Overleaf.

\subsection*{Architecture}

...diagram with the various \uwds clients

>>>>

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in {l2tor}  
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients
